Draft

### 2017-03-09 Draft/sections/misc-math.tex
[minor] About many wonderful formulae in exponential of matrices.

\subsection{Matrix Operations}
    \subsubsection{Matrix Exponentials}
    \label{sec:Matrix-Exponentials}
    \paragraph{The Zassenhaus formula}
    I found the formula from Wikipedia page:
    \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.
    \begin{align}
        e^{t(X+Y)} &= e^{tX}~ e^{tY} ~e^{-\frac{t^2}{2} [X,Y]} ~
        e^{\frac{t^3}{6}(2[Y,[X,Y]]+ [X,[X,Y]] )} \nonumber\\
        & \times
          e^{\frac{-t^4}{24}([[[X,Y],X],X] + 3[[[X,Y],X],Y] + 3[[[X,Y],Y],Y]) }
        \times\cdots
    \end{align}

>>>>

\subsection{Matrix Operations}
    \subsubsection{Matrix Exponentials}
    \label{sec:Matrix-Exponentials}

    \paragraph{Baker-Campbell-Hausdorf formula}
    I found the formula from Wikipedia page:
    \href{https://en.wikipedia.org/wiki/Baker%E2%80%93Campbell%E2%80%93Hausdorff_formula}{Baker–Campbell–Hausdorff formula}.

    \begin{align}
        Z(X,Y)&=\log(\exp X\exp Y) \nonumber\\
            &= X + Y + \frac{1}{2}[X,Y] +
            \frac{1}{12}\left ([X,[X,Y]] +[Y,[Y,X]]\right ) \nonumber\\
            &\quad
            - \frac {1}{24}[Y,[X,[X,Y]]] \nonumber\\
            &\quad
            - \frac{1}{720}\left([Y,[Y,[Y,[Y,X]]]] + [X,[X,[X,[X,Y]]]] \right)
            \nonumber \\
            &\quad +\frac{1}{360}\left([X,[Y,[Y,[Y,X]]]] + [Y,[X,[X,[X,Y]]]]\right)
            \nonumber\\
            &\quad
            + \frac{1}{120}\left([Y,[X,[Y,[X,Y]]]] + [X,[Y,[X,[Y,X]]]]\right)
            + \cdots
    \end{align}
    Also from the same source, we have:
    \paragraph{The Zassenhaus formula}
    \begin{align}
        e^{t(X+Y)} &= e^{tX}~ e^{tY} ~e^{-\frac{t^2}{2} [X,Y]} ~
        e^{\frac{t^3}{6}(2[Y,[X,Y]]+ [X,[X,Y]] )} \nonumber\\
        & \times
          e^{\frac{-t^4}{24}([[[X,Y],X],X] + 3[[[X,Y],X],Y] + 3[[[X,Y],Y],Y]) }
        \times\cdots
    \end{align}

    \paragraph{Hadamard's lemma}
    Again, from the same source, there is a useful formula (sometimes called
    \textit{Hadamard’s lemma}, see
    \href{http://www.physicspages.com/2016/11/17/exponentials-of-operators-hadamards-lemma/}{this
    page}.

    \begin{lemma}
        Let $G$ be a matrix Lie group, and $g$ its corresponding Lie algebra.
        Let $\mathrm{ad}_X$ be the linear operator on $g$ defined by
        $$\mathrm{ad}_X Y=[X,Y]=XY-YX$$
        for some $X\in g$. Denoted $\mathrm{Ad}_A$ for fixed $A\in G$ the linear
        transformation of $g$ given by $\mathrm{Ad}_A Y = AYA^{-1}$. We have:
        \begin{equation}
            \mathrm{Ad}_{e^X} = e^{\mathrm{ad}_X}
        \end{equation}
    \end{lemma}
    Explicitly,
    \begin{align}
        \mathrm{Ad}_{e^X}Y &= e^X Y e^{-X} = e^{\mathrm{ad}_X}Y  \nonumber\\
        &= Y + [X,Y] + \frac{1}{2!}[X,[X,Y]] + \frac{1}{3!}[X,[X,[X,Y]]] + \cdots
    \end{align}

    Sometimes the $\mathrm{ad}_X$ is denoted by \nomen{$[X,\,\,]$}, so that
    $[X,\,] Y=[X,Y]$. For example, this is used in p.138 of \cite{Altland2010}.
